Lattices of acyclic pipe dreams

### 2023-07-07 acyclicFacets/draft/latticePipeDreams.tex
small edit relating v-Tamari to increasing flip poset

In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated with $\nu$. The permutations of the form~$\omega_\nu$ can be easily characterized as follows. We refer to~\cite{CeballosPadrolSarmiento} for details.

The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrers diagram of a partition located at the top left corner $(1,1)$. Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding.
For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~${0, 1, \dots, n}$, and we consider here pipe dreams with pipes indexed by~${0, 1, \dots, n}$.

>>>>

In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(0\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated with $\nu$. The permutations of the form~$\omega_\nu$ can be easily characterized as follows. We refer to~\cite{CeballosPadrolSarmiento} for details.

The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrers diagram of a partition located at the top left corner $(1,1)$. Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding.
For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~${0, 1, \dots, n}$, and we consider here pipe dreams with pipes indexed by~${0, 1, \dots, n}$.
The $\nu$-Tamari lattice is the increasing flip poset on pipe dreams~$\pipeDreams(0\omega_\nu)$ for some dominant permutation $\omega_\nu$ determined by $\nu$, see~\cite{CeballosPadrolSarmiento}.
